\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-18 papers/jfp/1-intro.tex
Lift the contents of todo.md into the .tex and start to do the proposed splits
Rework the intro a bit

In this paper we offer a general framework in which to understand and compare
build systems, in a way that is both abstract (omitting incidental detail)
and yet precise (implemented as Haskell code). Specifically we make these
contributions:
\begin{itemize}
\item Build systems vary on many axes, including: static vs dynamic
  dependencies; local vs cloud; deterministic vs non-deterministic build tasks;
  support for early cutoff; self-tracking build systems; and the type of
  persistent build information. In~\S\ref{sec-background} we identify some key
  properties, illustrated by four carefully-chosen build systems.

@@

\item We identify two key design choices that are typically deeply wired into
  any build system: \emph{the order in which tasks are
  built}~(\S\ref{sec-dependency-orderings}) and \emph{whether or not a
  task is rebuilt}~(\S\ref{sec-out-of-date}). These choices turn out to
  be orthogonal, which leads us to a new classification of the design
  space~(\S\ref{sec-design-space}).

@@

\item Moreover, we can readily remix the ingredients to design new build systems
with desired properties, for example, to combine the advantages of \Shake and
\Bazel (\S\ref{sec-implementation-cloud}).

\end{itemize}
In short, instead of seeing build systems as unrelated
points in space, we now see them as locations in a connected landscape,
leading to a better understanding of what they do and how they compare,
and suggesting exploration of other (as yet unoccupied points) in the
landscape.
We discuss engineering aspects in \S\ref{sec-engineering}, and related
work in \S\ref{sec-related}.

>>>>

In this paper we give a general framework (refined from \cite{mokhov2018buildsystems}) in which to understand and compare
build systems, in a way that is both abstract (omitting incidental detail)
and yet precise (implemented as Haskell code). With this framework we can explain confusing details from the original Shake paper \cite{mitchell2012shake} and build new features useful for the GHC build system \cite{hadrian}. Specifically we make these contributions:
\begin{itemize}
\item Build systems vary on many axes, including: static vs dynamic
  dependencies; local vs cloud; deterministic vs non-deterministic build tasks;
  support for early cutoff; self-tracking build systems; and the type of
  persistent build information. In~\S\ref{sec-background} we identify some key
  properties, illustrated by four carefully-chosen build systems.

@@

\item We identify two key design choices that are typically deeply wired into
  any build system: \emph{the order in which tasks are
  built}~(\S\ref{sec-scheduler}) and \emph{whether or not a
  task is rebuilt}~(\S\ref{sec-rebuilder}). These choices turn out to
  be orthogonal, which leads us to a new classification of the design
  space~(\S\ref{sec-design-space}).

@@

\item Moreover, we can readily remix the ingredients to design new build systems
with desired properties, for example, to combine the advantages of \Shake and
\Bazel (\S\ref{sec-cloud-shake}), and evaluate the result (\S\ref{sec-experience}).

\end{itemize}
In short, instead of seeing build systems as unrelated
points in space, we now see them as locations in a connected landscape,
leading to a better understanding of what they do and how they compare,
and making it easier to explore other points in the
landscape.
We discuss engineering aspects in \S\ref{sec-engineering}, and related
work in \S\ref{sec-related}.
